% This file was produced automatically, edit footnotes in messy_main_tracer_chemprop.tbl, not here!
\item {\bf  O2:} Estimate.
\item {\bf  O3:} Value measured at 292 \unit  {K}.
\item {\bf  OH:} Value measured at 293 \unit  {K}.
\item {\bf  HO2:} Value for aqueous salts at 293 \unit  {K}.
\item {\bf  NH3:} Value measured at 295 \unit  {K}.
\item {\bf  NO:} Value measured between 193 and 243 \unit  {K}.
\item {\bf  NO2:} Value measured at 298 \unit  {K}.
\item {\bf  NO3:} Value is a lower limit, measured at 273 \unit  {K}.
\item {\bf  N2O5:} Value for sulfuric acid, measured between 195 and 300 \unit  {K}.
\item {\bf  HONO:} Value measured between 247 and 297 \unit  {K}.
\item {\bf  HNO3:} Value measured at room temperature. \citet  {930} say $\gamma >0.2$. Here $\alpha =0.5$ is used.
\item {\bf  HNO4:} Value measured at 200 \unit  {K} for water ice.
\item {\bf  CH3O2:} Estimate.
\item {\bf  CO2:} Estimate.
\item {\bf  HCHO:} Value measured between 260 and 270 \unit  {K}.
\item {\bf  PAN:} Estimate.
\item {\bf  C2H5O2:} Estimate.
\item {\bf  CH3CHO:} Using the same estimate as in the CAPRAM 2.4 model \citep  {2573}.
\item {\bf  HCl:} Temperature dependence derived from published data at 2 different temperatures
\item {\bf  HOCl:} Assumed to be the same as $\alpha $(HOBr).
\item {\bf  ClNO3:} Value measured at 274.5 \unit  {K}.
\item {\bf  HBr:} Temperature dependence derived from published data at 2 different temperatures
\item {\bf  HOBr:} Value measured at room temperature. \citet  {930} say $\gamma >0.2$. Here $\alpha =0.5$ is used.
\item {\bf  BrNO3:} Value measured at 273 \unit  {K}.
\item {\bf  BrCl:} Assumed to be the same as $\alpha $(Cl2).
\item {\bf  I2:} Estimate.
\item {\bf  IO:} Estimate.
\item {\bf  OIO:} Estimate.
\item {\bf  I2O2:} Estimate.
\item {\bf  HI:} Temperature dependence derived from published data at 2 different temperatures
\item {\bf  HOI:} Assumed to be the same as $\alpha $(HOBr). See also \citet  {1565} and \citet  {1572}.
\item {\bf  HIO3:} Estimate.
\item {\bf  INO2:} Estimate.
\item {\bf  INO3:} Estimate.
\item {\bf  ICl:} Estimate.
\item {\bf  IBr:} Assumed to be the same as $\alpha $(ICl).
\item {\bf  H2SO4:} Value measured at 303 \unit  {K}.
\item {\bf  Hg:} Estimate.
\item {\bf  HgO:} Estimate.
\item {\bf  HgCl2:} Estimate.
\item {\bf  HgBr2:} Estimate.
\item {\bf  ClHgBr:} Estimate.
\item {\bf  BrHgOBr:} Estimate.
\item {\bf  ClHgOBr:} Estimate.
